Model

### 2019-06-09 stats/model.Rmd
update model plotting

  var speakerOptimalityParameters = {
    intercept: uniformDrift({a: -2, b: 2, width: 0.5}),
    slope: uniformDrift({a: 0, b: 2, width: 0.5})
  }

  var globalLineParameters = {
    intercept: uniformDrift({a: -3, b: 3, width: 1}),
    slope: uniformDrift({a: 0, b: 3, width: 1})
  }

@@

# sem_know_model<- webppl(
#   program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
#   data = list(data = me_model_data),
#   data_var = "dataFromR",
#   model_var = "model",
#   chains = 8,
#   cores = 8,
#   inference_opts = list(method = "incrementalMH", 
#                         samples = 4000, 
#                         burn = 2000,
#                         verbose = T,
#                         lag = 1,
#                         verboseLag = 1000)
# )

@@

# 3 chains, 6000 iterations per chain, 2000 burn in, lag = 1
sem_know_model <- readRDS("../saves/sem_know_model.rds")
# 8 chains, 4000 iterations per chain, 2000 burn in, lag = 1
sem_know_model <- readRDS("../saves/sem_know_model_2.rds")
```

@@

### Comparing sem knowledge parameters between model runs

@@

ggplot(run_comp, aes(x = age+2, y= sem_know, fill = run, group = paste(run,Chain)))+
  geom_line(size = .3, aes(col = run))+
  geom_ribbon(aes(ymin=sem_know_lci, ymax = sem_know_uci), alpha = .1)+
  ylab("Semantic knowledge")+
  xlab("Age")+
  ylim(0,1)+
  facet_wrap(~item)+
  theme_few()+
  scale_colour_solarized()+
  scale_fill_solarized()

ggsave("../graphs/model_by_chain_run.pdf", width = 10, height = 8)
```

# Inverse predictions

>>>>

  var speakerOptimalityParameters = {
    intercept: uniformDrift({a: -2, b: 2, width: 0.5}),
    slope: uniformDrift({a: 0, b: 1, width: 0.5})
  }

  var globalLineParameters = {
    intercept: uniformDrift({a: -3, b: 3, width: 0.5}),
    slope: uniformDrift({a: 0, b: 2, width: 0.5})
  }

@@

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
  data = list(data = me_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 4,
  cores = 4,
  inference_opts = list(method = "incrementalMH",
                        samples = 6000,
                        burn = 2000,
                        verbose = T,
                        lag = 1,
                        verboseLag = 1000)
)

@@

# 3 chains, 6000 iterations per chain, 2000 burn in, lag = 1
sem_know_model <- readRDS("../saves/sem_know_model.rds")
# 8 chains, 4000 iterations per chain, 2000 burn in, lag = 1
sem_know_model <- readRDS("../saves/sem_know_model_2.rds")

sem_know_model <- sem_know_model %>%
  filter(Chain != "1")
```

@@

### Comparing parameters between model runs

#### sem knowledge

@@

ggplot(run_comp, aes(x = age+2, y= sem_know, fill = run, group = paste(run,Chain)))+
  geom_line(size = .3, aes(col = run))+
  geom_ribbon(aes(ymin=sem_know_lci, ymax = sem_know_uci), alpha = .1)+
  ylab("Semantic knowledge")+
  xlab("Age")+
  ylim(0,1)+
  facet_grid(item~run)+
  theme_few()+
  scale_colour_solarized()+
  scale_fill_solarized()

ggsave("../graphs/model_by_chain_run.pdf", width = 3, height = 12, scale = 1.5)
```

#### speaker optimality

# 3 chains, 6000 iterations per chain, 2000 burn in, lag = 1
so_run_1 <- readRDS("../saves/sem_know_model.rds")%>%
  separate(Parameter, into = c("parameter", "type","token"), sep = ",")%>%
  filter(parameter == "parameter", type == "parameters", token == "speaker_optimality")%>%
  separate(value, into = c("int", "slope"),sep = ", ")%>%
  mutate(int = as.numeric(str_remove_all(int, "[(c]")),
         slope = as.numeric(str_remove(slope, "[)]")))%>%
  mutate(run = "1")

# 8 chains, 4000 iterations per chain, 2000 burn in, lag = 1
so_run_2 <- readRDS("../saves/sem_know_model_2.rds")%>%
  separate(Parameter, into = c("parameter", "type","token"), sep = ",")%>%
  filter(parameter == "parameter", type == "parameters", token == "speaker_optimality")%>%
  separate(value, into = c("int", "slope"),sep = ", ")%>%
  mutate(int = as.numeric(str_remove_all(int, "[(c]")),
         slope = as.numeric(str_remove(slope, "[)]")))%>%
  mutate(run = "2")

so_run_iteration <- bind_rows(
   so_run_1,
   so_run_2)

so_run_summary <- so_run_iteration%>%
  group_by(run,Chain)%>%
  summarise(overall_int = estimate_mode(int),
            overall_slope = estimate_mode(slope))

so_run <- so_run_iteration %>%
  left_join(so_run_summary)

so_run_comp <-so_run%>%
  group_by(run,Chain,Iteration)%>%
  expand(int,slope,overall_int,overall_slope,age = unique(me_model_data$age))%>%
  mutate(so_ci = int + slope * age,
         so = overall_int + overall_slope * age) %>%
  group_by(run,Chain, age) %>%
  summarise(so = estimate_mode(so), 
            so_uci = hdi_upper(so_ci),
            so_lci = hdi_lower(so_ci))

ggplot(so_run_comp, aes(x = age+2, y= so, fill = run, group = paste(run,Chain)))+
  geom_line(size = .3, aes(col = run))+
  geom_ribbon(aes(ymin=so_lci, ymax = so_uci), alpha = .1)+
  ylab("speaker optimality")+
  xlab("Age")+
  facet_grid(~run)+
  theme_few()+
  scale_colour_solarized()+
  scale_fill_solarized()

ggsave("../graphs/model_by_chain_run.pdf", width = 3, height = 12, scale = 1.5)
```
# Inverse predictions
